\section{Business Context}

\subsection{Stakeholder Profiles}
% This section describes who will benefit from the product both directly and 
% indirectly.  Identify stake holders by their roll and describe their needs and
% interactions for that role.

Our stakeholders vary depend on who ends up recording video snippets, but in general they consist of our customer (Dr Jagodzinski), 
WWU Alumni, WWU Clubs, and WWU Students/Staff.

We get the to work with our most important client Dr. Jagodzinski to make a product that 
is appealing to him and the CS department, and possibly other departments also.

The WWU Alumni are the subject and target demographic of this project, so they also are a large stakeholder. Because they are
what this project is made of, we need to make sure we accomodate their needs and take in their feedback as we record video snippets and 
continue development. Overall, Alumni (specifically donors) are what will help us figure out the right way to reach other donors successfully.

The students, faculty, and clubs of the WWU Computer Science Department are stakeholders in this project as well, since the success of this project can impact 
them in a positive way via funds for scholarships and improved technology and resources in their classes. 
They also may record video snippets for us, so once again we want to make sure we accomodate their needs and gather feedback from them.

\subsection{Project Priorities}
% Prioritize the major features identified above based on the relative
% return-on-investment.  

For this project, there are 3 main priorities
1. Be able to stitch together snippets to create videos
2. Have a system to automatically upload videos to a specified location and generate a unique URL
3. Have a backlog of snippets to use to make created videos more diverse

\subsection{Operating Environment}
% Describe how and where the product will be used.  

This product will be used in an online setting, to hopefully encourage potential donors to donate. 
The program will take in names and e-mails, store the information ina database, and then send out emails with URLs in 
them that direct the client to a personalized video.
