\section{Deliverables}
% The purpose of this section is to formally list the major components that you
% will produce as part of this project.

\subsection{Software/Hardware}
% List the software components and hardware, if any, that you will deliver as
% part of this project. 
There are 3 major components, (1) the collection of clips, (2) the processing of clips,
and (3) the stitching of videos.
\begin{enumerate}
    \item The collection of clips will be done manually and in person, where we will
    reserve a room, ideally in the Communication Facility on the Western Washington
    University campus, and encourage students and staff to show up and film clips.
    By the end of the recording session, we will have clips of a student saying 
    their name and various words we prompt them with cue cards. As well as a 
    release form signed and filled out by each student.
    \item We are also developing a program that takes in unedited clips and edits 
    them down to single word clips, names them, then stores them in the directory 
    with the rest of the edited clips.
    \item Finally, we will also create a program that stitches our edited clips
    together. It accepts a CSV file, where each line contains the alumni's first 
    name, last name, and grad year. The program creates a personalized video for 
    each alumnus requesting a donation to the department. The program will store 
    the video in an encrypted URL and copies the CSV file and appends each alumnus's
    URL to the end of their line.
\end{enumerate}

\subsection{Documentation}
% What user documentation will you deliver.
Our programs will be stored on GitLab where our client Jagodzinski has maintainer
access. How to use each program will be found in the readme file, which will state 
the arguments and their formats, as well as what is expected to be returned.\\
We will also provide a pdf that contains how to collect video clips. Namely, the 
process for scheduling sessions, collecting and submitting waivers, reaching out 
to the department to get people to show up, and how to conduct the recording session.

\subsection{Key Presentations}
% You will present your project at the end of 492 and 493.
For 492 we will plan to have the stitching software nearly complete, how we went 
about collecting videos, as well as how we process unedited clips.\\
For 493 our project should be complete as we hope to have it ready to go by give day.
We would be able to showcase how give day went and talk about any issues we had to
address or features we added to incorporate feedback on its performance to improve 
it for next give day.

\subsection{Other Deliverables}
% Are there any other deliverables like in-person training?
Not applicable in our project.
