\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[normalem]{ulem}
\usepackage[left=3cm, right=3cm, top=2cm]{geometry}

\title{Alumni Video Donations M9}
\author{Simone Davison, Andrew Lanum, and Austin Morin }
\date{May 18, 2022}

\begin{document}

\maketitle

\section{General Progress Report}
As of May 18, the project will be in its final stages of development as we prepare 
for our end-of-the-year presentations this coming week. The program-breaking bugs 
from the last milestone have been squashed, and we are preparing to input over 2,000 
WWU donors through our Python program so that the final stitched videos can be sent 
out to them before Give Day on May 26th. This will require the Alumni team to split 
the input entry amongst themselves and closely monitor run-time performance and any 
bugs that might happen during the weaving process. The majority of the work done 
between this milestone and the last milestone was having our program reviewed 
by Dr. Jagodzinski and updating video content, images, and clips where required. 
The main intuition behind this was to ensure that there we unique clips for three 
types of recipients: recent graduate alumni, older graduate alumni, and non-alumni. 
Jagodzinski will also perform some basic CSS and formatting maintenance on the webpage 
before having our team deploy the final version of it online. Some additional 
last-minute video footage was recorded as well. The weaving program was updated 
so that multiprocessing passes less data between processes to speed up performance 
and saves work if the program happens to crash. It can also distinguish between different image types and handle those accordingly to avoid visual bugs during video weaving.\\~\\Some things that yet to be completed before the 
end of the quarter is writing a user's guide that will instruct faculty and future students 
working on the project on how to use the content found in both our GitLab and Google Firebase 
repositories. Code and files will undergo one final look and be cleaned up, organized, and 
commented thoroughly and feedback from post-Give Day activities will be assessed.

\section{Team Accomplishments}
\begin{itemize}
    \item Formatted and split up xlsx files from client to be used in final project
    \item Updated program to run more smoothly with multiprocessing and keep track of where it was if it exits in the middle of running
    \item Reformatted and updated website layout to be more visually pleasing and user-friendly
    \item Added and removed clips to make videos more coherent
    \item Ran multiple large-scale tests to ensure program can run on a large scale
    \item Began process of cleaning up code to make sure the program is readable for another group in the future
\end{itemize}

\section{Goals Met}
\begin{itemize}
    \item Video content and formatting is completed. Project is ready for final performance and operation checks.
\end{itemize}

\section{Goals Not Met}
\begin{itemize}
    \item All 2000+ donation videos not built and uploaded to Firebase.
    \item All videos sent out to donors.
    \item Have the website completely designed (able to put attention towards videos as links are not going out until May 25)
    \item Finalize copyright and ownership rights to the project and create a final credits/acknowledgements list.
    \item Finish user documentation.
    \item Demo the program usage to our client.
    \item Completely clean code, files, and file structures within Google Firebase and the Gitlab repo.
\end{itemize}

\section{Updated Expectations}
See section Quarter Plan below for more details
\begin{itemize}
    \item Weeks 7-9:
    \begin{itemize}
        \item Finish designing videos
        \item Make the videos
        \item Give administration the XLSX file of donors and video links
        \item Clean up/comment code
        \item Documentation
        \item Prepare and give the 493 presentation
    \end{itemize}

    \item Weeks 10-11:
    \begin{itemize}
        \item Incorporate feedback from give day
        \item Clean up/comment code
        \item Documentation
    \end{itemize}
\end{itemize}

\section{Branch Description}
    \begin{itemize}
        \item master - All the most current project work is pushed to this branch (code, resources, documentation, etc.)
        \item MS-2 - All project work pushed before Milestone 2’s date.
        \item MS-3 - All project work pushed before Milestone 3’s date.
        \item MS-4 - All project work pushed before Milestone 4’s date.
        \item MS-5 - All project work pushed before Milestone 5’s date.
        \item MS-6 - All project work pushed before Milestone 6’s date.
        \item MS-7 - All project work pushed before Milestone 7’s date.
        \item MS-8 - All project work pushed before Milestone 8’s date.
        \item MS-9 - All project work pushed before Milestone 9’s date.
    \end{itemize}
    
\section{Quarter Plan}
\begin{itemize}
    \item Week 1 (Mar 28 - Apr 1)
    \begin{itemize}
        \item Multiprocessing
        \item Refine videos
        \item Update CSV reference in program
        \item \sout{Add access tokens} (unnecessary for our project)
        \item Test on videos 2-30 (with upload turned off)
    \end{itemize}
    \item Week 2 (Apr 4 - Apr 8)
    \begin{itemize}
        \item MS6 (Have access token working, make headway on multiprocessing)
        \item Multiprocessing
        \item Refine videos
        \item Begin hosting website on Firebase
        \item Test on videos 2-30 (with upload turned off)
    \end{itemize}
    \item Week 3 (Apr 11 - Apr 15)
    \begin{itemize}
        \item Multiprocessing
        \item Refine videos
        \item Refine website hosted by Firebase
        \item \sout{Test on videos ~1000 (with upload turned off)} (Moved to week 4)
    \end{itemize}
    \item Week 4 (Apr 18 - Apr 22)
    \begin{itemize}
        \item MS7 (Have multiprocessing working and video content well organized)
        \item Refine videos
        \item Refine website
        \item Begin development on an installable executable
        \item Test on videos ~1000 (with upload turned off)
        \item Begin full scale testing (10,000 videos) (expected to take a while)
    \end{itemize}
    \item Week 5 (Apr 25 - Apr 29)
    \begin{itemize}
        \item Monitor video making process (fix bugs)
        \item Let client try product
        \item Inspect output videos
        \item Improve program
        \item Refine videos
        \item Refine website
        \item \sout{Begin development on an installable executable} (Moved to week 4)
    \end{itemize}
    \item Week 6 (May 2 - May 6)
    \begin{itemize}
        \item MS8 (Have begun refining documentation, \sout{have website hosted by Firebase} (already accomplished), have an installable executable)
        \item Full scale test again (10,000 videos) (expected to take a while)
        \item Refine videos
        \item Refine website
    \end{itemize}
\item Week 7 (May 9 - May 13)
    \begin{itemize}
        \item Documentation
        \item Refine videos
        \item Refine website
    \end{itemize}
    \item Week 8 (May 16 - May 20)
    \begin{itemize}
        \item MS9 (Finish designing videos and begin production)
        \item Documentation
        \item Refine videos
        \item Refine website
        \item Make the videos this week and over the weekend
        \item Monitor created videos
    \end{itemize}
    \item Week 9 (May 23 - May 27)
    \begin{itemize}
        \item Hand over the XLSX file containing donors and links to videos to CS administration
        \item Documentation
        \item Clean up/comment code
        \item Refine website
        \item Prepare for presentation
        \item Videos sent out for give day (May 25-26)
        \item Present! (May 27)
    \end{itemize}
    \item Week 10 (May 30 - Jun 3)
    \begin{itemize}
        \item Documentation
        \item Clean up/comment code
        \item Use feedback to from give day to improve product
    \end{itemize}
    \item Week 11 (Jun 6 - Jun 10)
    \begin{itemize}
        \item Documentation
        \item Clean up/comment code
    \end{itemize}
\end{itemize}

\section{Team Member Accomplishments}
\begin{itemize}
    \item  \bf{Simone Davison - (Hours Worked: 23)}
    \begin{itemize}
        \item Updated multiprocessing to pass less data between processes. Now it is stored in a file.
        \item Learned to not bog down other lab machines by running the program in TMP.
        \item Recorded more videos.
        \item Program now saves work upon crash.
        \item Cleaned up final excel file of recipients.
    \end{itemize}
    
    \item  \bf{Andrew Lanum - (Hours Worked: ~8)}
		\begin{itemize}
			\item Added music to make videos more professional
			\item Fixed resolution bug that caused black bars to appear sometimes
			\item Ran a large scale test successfully
			\item Updated text and made new QR code ad to better meet client specifications
			\item Began deleting unused or otherwise useless code
			\item Removed strange and/or unusable clips from firebase
		\end{itemize}
		
    \item  \bf{Austin Morin - (Hours Worked: 15.5 hours)}
    \begin{itemize}
        \item Changed website wording and messages that dynamically change depending on the user's name.
        \item Added play button overlay to video.
        \item Debugged weave.py and ran a 50-video sample and tracked runtime.
        \item Created some final bonus videos.
        \item Started code cleaning.
    \end{itemize}
\end{itemize}

\end{document}


\end{document}
