\section{Glossary}

1) CSV - A text file that uses a comma to separate values. Each line of the file is a data record. Each record consists of one or more 
fields, separated by commas. Typically represents data to be inserted into a database. Microsoft Excel is an example of software that
accepts CSV files. (Source - https://en.wikipedia.org/wiki/Comma-separated_values)\\~\\

2) moviepy - A Python programming language library for video editing that supports cutting, concatenations, title insertions, video compositing, 
video processing, and creation of custom effects. (Source - https://pypi.org/project/moviepy/)\\~\\

3) pydub - A Python programming language library that allows users to edit audio files.\\~\\

4) QR-Code - A type of barcode that can be read easily by a digital device and which stores information as a series of pixels in a square-shaped grid.
QR codes can include website URLs, phone numbers, store up to 4,000 characters of text, link directly to download an app on the Apple App 
Store or Google Play, authenticate online accounts and verify login details, access Wi-Fi by storing encryption details such as SSID, password, 
and encryption type, send and receive payment information, and more. 
(Source - https://usa.kaspersky.com/resource-center/definitions/what-is-a-qr-code-how-to-scan)\\~\\

5) VPN - A virtual private network (VPN) gives you online privacy and anonymity by creating a private network from a public internet connection. 
VPNs mask your internet protocol (IP) address so your online actions are virtually untraceable. Most important, VPN services establish 
secure and encrypted connections to provide greater privacy than even a secured Wi-Fi hotspot. 
(Source - https://us.norton.com/internetsecurity-privacy-what-is-a-vpn.html)\\~\\

6) Race condition - A race condition is an undesirable situation that occurs when a device or system attempts to perform two or more operations at the same time, 
but because of the nature of the device or system, the operations must be done in the proper sequence to be done correctly.\\~\\

