\section{Introduction}
% This section is used for multiple kinds of documents.  It describes the
% purpose of this document in the context of the rest of the product's
% documentation library.  

This document serves to show a more detail-oriented description of how the Alumni-Money project will work.
It will show off features, as well as go into how the program is intended to be run.

\subsection{Purpose}
% What is the purpose of this document as opposed to the vision and scope,
% software design document (492), testing plan (493), et al.

The purpose of this document is to show how the Alumni-Money project runs on a more low-level basis.
It's not quite as in-depth as pseudocode, but not as abstract as a vision and scope document.

\subsection{Document Conventions}
% Describe the conventions used in this document.  For example, throughout this
% document, the use of the plural shall imply the singular unless otherwise
% stated.  Now you can avoid parenthetical plurals like student(s).   
Throughout this document, a 'snippet' refers to a smaller video that has been created out of a larger video.
Throughout this document, a 'stitched video' refers to a video that is composed of snippets played in succession.
Throughout this document, hashing and encrypting may be used interchangably, but the plan is to use hashing rather than full-scale encryption.

\subsection{Intended Audience and Reading Suggestions}
% Formally state the intended audience for this document.  For the SRS, the
% audience is usually developers, quality control, and documentation.  You are
% free to describe whatever readers you feel are appropriate, but you should not
% describe the reader in terms of the class.  That is, do not refer to a teacher
% or other students.  
The intended audience of this document is anybody who plans to use the Alumbi-Money project regularly, or needs help understanding
 how the project works. This will likely be developers, quality control, or possibly a customer.
 
When reading this document, it is suggested that the reader has or quickly develops a basic understanding of the basic principles 
 of computer science and software creation.

\subsection{Project Scope}
% Put this developed project in the context of the overall product.  This is a
% brief summary of the vision and scope.  Just enough for the reader to
% understand the context for the requirements in later sections.
The goal of this project is to provide an easy-to-use system that allows the WWU CS department to mass-email personalized videos
 to alumni of the CS deparment soliciting donations. The videos will be created out of snippets of alumni, students, and staff
 saying specific words and phrases, and possibly giving some anecdotal accounts of their time at WWU.

\subsection{References}
% List other documents that you refer to in the rest of this document.  Include
% unreferenced, but important documents for the project.  

Documentation for python modules used in this project:
moviepy: https://pypi.org/project/moviepy/
pydub: https://pydub.com/
